Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/evaluation.tex

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for our
dataset (27 for the UW dataset) with a maximum of 2,744 (659 for
UW). The average number of jumps per trace is 3 (also 3 for
UW) with a maximium of 177 (52 for UW). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%

>>>>

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for our
dataset (27 for the \uwbench\ dataset) with a maximum of 2,744 (659 for
\uwbench). The average number of jumps per trace is 3 (also 3 for
\uwbench) with a maximium of 177 (52 for \uwbench). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%
